Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-10 paper_jasa.tex
small things

The actual data plot is generated by making a scatterplot of $Y$ vs $X_1$ with the least squares regression line overlaid. To produce the null plots in the lineup null data was simulated from $N(X \hat{\beta}, {\hat{\sigma}}^2$) and plotted using the same scatterplot method as the actual data. 
An example lineup from this experiment is shown in Figure \ref{fig:test_continuous}.  This lineup is generated using sample size ($n$)=100, slope($\beta$)=1.25 and and error SD($\sigma$)=5. The actual data plot location is 11. This lineup, we think, is a difficult one. To select 10 lineups for a subject, each combination of sample size ($n$) and error SD ($\sigma$) is given a difficulty value based on the slope ($\beta$) parameters. For the smallest slopes the difficulty is 4 (hardest) and for the largest slopes the difficulty is 0 (easiest). For one combination of sample size and standard deviation, the subject sees a randomly selected lineup of each difficulty level, all the slopes, giving 5 lineups. Another four lineups are chosen from a second choice of sample size and standard deviation, with difficulty levels 0-3, and the last lineup shown was a randomly selected lineup with difficulty 0. The order that the lineups are shown to participants is randomized. Each subject saw a substantial number of difficult lineups. The intention was noble, to get a better handle on the power of the lineups for small slopes, but practically this made is very tiring for the participants. It would be better to provide the subjects with a larger selection of easier lineups and just a few difficult ones. \green{perhaps should go into so much detail about this, or keep this for the conclusions section.}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
       \caption{p-value vs plot signal strength. The solid line represents 45 degree line which represents the equity shown in equation \ref{plot_signal}}
       \label{fig:pval_plot_signal}
\end{figure*}

>>>>

The actual data plot is generated by making a scatterplot of $Y$ vs $X_1$ with the least squares regression line overlaid. To produce the null plots in the lineup null data was simulated from $N(X \hat{\beta}, {\hat{\sigma}}^2$) and plotted using the same scatterplot method as the actual data. 
An example lineup from this experiment is shown in Figure \ref{fig:test_continuous}.  This lineup is generated using sample size ($n$)=100, slope($\beta$)=1.25 and and error SD($\sigma$)=5. The actual data plot location is 11. This lineup, we think, is a difficult one. To select 10 lineups for a subject, each combination of sample size ($n$) and error SD ($\sigma$) is given a difficulty value based on the slope ($\beta$) parameters. For the smallest slopes the difficulty is 4 (hardest) and for the largest slopes the difficulty is 0 (easiest). For one combination of sample size and standard deviation, the subject sees a randomly selected lineup of each difficulty level, all the slopes, giving 5 lineups. Another four lineups are chosen from a second choice of sample size and standard deviation, with difficulty levels 0-3, and the last lineup shown was a randomly selected lineup with difficulty 0. The order that the lineups are shown to participants is randomized. Each subject saw a substantial number of difficult lineups. \hh{While this allows us a better estimation for the power in small slopes, }
%The intention was noble, to get a better handle on the power of the lineups for small slopes, 
but practically this made the study very tiring for the participants. %It would be better to provide the subjects with a larger selection of easier lineups and just a few difficult ones. 
\green{perhaps should go into so much detail about this, or keep this for the conclusions section.}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
       \caption{$p$-value vs plot signal strength. The solid line represents 45 degree line which represents the equity shown in equation \ref{plot_signal}
       \hh{Mahbub, could you exchange this plot for one with  $p_D$ estimated as $(1 - \#  correct/ \# shown)/(m-1)$ as given in lemma 3.1 now?}}
       \label{fig:pval_plot_signal}
\end{figure*}
